Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-30 Paper/results.tex
Start of results
Jed made some minor edits

\section{Results}
\subsection{Nations Over Time}

@@

The United States and China are shown here and exhibit some dramatic
differences. First, it is worth pointing out that the United States has many
more ASes than China, hence it's line extends further to the right in these
plots. We also see that China, in all cases, can control a much larger portion
of its paths with much fewer ASes than the United States. This result is
entirely expected. Of more interest is the trends that can be seen over time.
The AS-level topology of China's Internet has evolved such that very few ASes
can intercept nearly all BGP paths. The US has evolved in a different way.
While it has become somewhat easier for the US to intercept most of its paths,
it has become more difficult to intercept around 70\% of its paths and higher.
This suggest an expansion of ASes on the interior and more connections, as well
as a strengthening of the very top ASes.

>>>>

\section{Results}

In this section we present the results of several experiments aimed at
answering the questions presented in Section~\ref{sec:exp}.

\Ben[inline]{We should answer the questions in the order we ask them. 1)
National Chokepoint potential and implications. 2) Comparison among nations. 3)
Evoluation over time.}

\subsection{National Chokepoint Potential}

\Ben[inline]{Include results here about general chokepoint potential,
currently}.

\subsection{Nations Over Time}

@@

The United States and China are shown here and exhibit some dramatic
differences. First, it is worth pointing out that the United States has many
more ASes than China, hence its line extends further to the right in these
plots. We also see that China, in all cases, can control a much larger portion
of its paths with much fewer ASes than the United States. This result is
entirely expected. Of more interest is the trends that can be seen over time.
The AS-level topology of China's Internet has evolved such that very few ASes
can intercept nearly all BGP paths. The US has evolved in a different way.
While it has become somewhat easier for the US to intercept most of its paths,
it has become more difficult to intercept around 70\% of its paths and higher.
This suggest an expansion of ASes on the interior and more connections, as well
as a strengthening of the very top ASes.
